Cloud Manufacturing xxx from a ecosystem view

### 2016-03-07 background.tex
细微调整结构框架，准备开始框架修改和文献综述并行。
阶段性定框架
add the enterprise model
start the report

% section problem_background (end)

>>>>

\subsection{Cloud Manufacturing Ecosystem} % (fold)
\label{sub:cloud_manufacturing_ecosystem}

Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

\subsubsection{Enterprise Business Mode}

\subsubsection{Resource Sharing Mechanism}

\subsubsection{Ecosystem Adjustment}

% subsection cloud_manufacturing_ecosystem (end)

\subsection{Main Copmlexity Concepts} % (fold)
\label{sub:main_copmlexity_concepts}

\subsubsection{Self-organization}

\subsubsection{Emergence}

\subsubsection{Co-evolution}

\subsubsection{Adaption}
% subsection main_copmlexity_concepts (end)

\subsection{Ecosystem Evolvement} % (fold)
\label{sub:ecosystem_evolvement}

% subsection ecosystem_evolvement (end)

\subsection{Optimal Guidance} % (fold)
\label{sub:optimal_guidance}

% subsection optimal_guidance (end)
% section problem_background (end)

### 2016-03-07 method.tex
增加生态系统功能框架，文献综述
阶段性定框架
add the enterprise model
start the report

\subsection{Model Assumptions and Notation} % (fold)
\label{sub:model_assumptions}

% subsection model_assumptions (end)

\subsection{Mathematical Formulation} % (fold)
\label{sub:mathematical_formulation}

% subsection mathematical_formulation (end)

>>>>

\subsection{Modeling} % (fold)
\label{sub:modeling}

\subsubsection{Assumptions and Notation}

Ecosystem application model including:
\subsubsection{Enterprise Model}

The Model can be described with two main parts, namely object itself(attribute) and the interaction with other enterprises(function or method)

Users from platform managers, enterpirse users, customers. Even though they characteristic can be overlaped. just inherent it.

Enterprise can be described as the object with attributes like 
\begin{itemize}
	\item Rank(reputation)
	\item Resources(type, quantity, quality)
	\item Capbility
	\item Processing Status
\end{itemize}

\subsubsection{System Model}
\begin{itemize}
	\item Coevolution
	\item Self-organization
	\item Emergence	
	\item Adaption
\end{itemize}

Coevolution consist of:
\begin{itemize}
	\item Scarcity of customers
	\item Conscious choice that enables the organizations to change
	\item Interconnectedness of the enables the organizations to change
	\item Feedback processes that carry the long-term consequences of coevolution
\end{itemize}

\subsubsection{Management Model}

% subsection modeling (end)

\subsection{Mathematical Formulation} % (fold)
\label{sub:mathematical_formulation}
\subsubsection{Comprehended Model}
% subsection mathematical_formulation (end)

### 2016-03-07 review.tex
细微调整结构框架，准备开始框架修改和文献综述并行。
阶段性定框架
add the enterprise model
start the report

% section literature_review (end)

>>>>

\subsection{Business Mode} % (fold)
\label{sub:business_mode}

% subsection business_mode (end)

\subsection{Cloud Manufacturing} % (fold)
\label{sub:cloud_manufacturing}
% This definition is quite abstract and thus despite its corretness not very useful.
from \textbf{function, resource}, information, process view to depict the cloud manufacturing platform.

Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (Tao, Zhang, et al. 2012;Valilai and Houshmand 2013)
% subsection cloud_manufacturing (end)

\subsection{Manufacturing Ecosystem} % (fold)
\label{sub:manufacturing_ecosystem}
% xx of an ecosystem is a path-dependent, chaotic process, which means that a small difference in starting values can cause great difference to result.

% From a bionomic perspective, organisms and organizations are nodes in networks of relationships. As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network. 
\subsubsection{Different Ecosystem Analogies}

\subsubsection{Manufacturing System}
% Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.

% coevolved to form a vast living ecosystem

% 4 different stages for ecosystem:
% birth, expansion, leadership, final(self-renew or death)

% the major difference between ecological and social system is the role of conscious choice.

% Accoring to xxx there are three critical success factors of a business ecosystem.
% First, productivity
% Second, Robustness
% Third, have the ability to create niches and opportunities for new firms.

% Complexity relevant concepts

% Self-organization
% Emergence
% Coevolution
% adaptation

% subsection manufacturing_ecosystem (end)

\subsection{Complex System} % (fold)
\label{sub:complex_system}
\subsubsection{System Dynamic}

\subsubsection{Cellular Automata}
% subsection complex_system (end)
% section literature_review (end)
